\section{}
\subsection{(45 min)}
% https://davekilian.com/acquire-release.html
Consider a 'fence' operation. This provides a 'synchronization point,' such that all memory operations before and after the fence wait for all others, and once all operations meet at the fence, they tear it down. 
Now, consider propping a ladder up on one side of the metaphorical fence. For an acquire or release, this synchronization is 'one-way,' so anyone on the far side cannot access until the last operation throws the ladder over the fence. 

\subsection{(3 hrs)}
I implemented Message Passing with pthreads and acquire/release semantics. 
This program has a writer thread which writes two values in succession with a release between the writes, 
and then a reader thread which reads those respectively with an acquire fence between them. 
Pthreads only allows one arg so I wrapped the values in a struct. 
The release/acquire semantics ensure that x=1,y=1 always holds at termination, but does not force the writer to wait for respective read. 

\lstinputlisting[caption={MessagePassing}, label={lst:MP}]{../ctests/raq.c}

\subsection{(5 min)}
In a certain sense, this is consistent, we have DMB ISH for the release and DMB ISHLD for the acquire. 
In another sense, this is redundant, as we are using atomics and the compiler uses stlr and ldar, which enforce sequential consistency anyhow. 
Overall this is indeed consistent, albeit redundant. \newline
Here is the compiled code (screenshots in appendix):

\lstinputlisting[caption={Compiled MessagePassing}, label={lst:MPC}]{../logs/q3/raq.txt}

\subsection{(10 min)}
Litmus test of the above:
\lstinputlisting[caption={MP with Release/Acquire Litmus}, label={lst:mpraq}]{../mpraq.litmus}

\subsection{(15 min)}
As above, we expect and see 'forbidden' here, we have this doubly redundant synchronization with fences and store-releases. 
\begin{lstlisting}
    cd ctests
    herd7 ../mpraq.litmus > ../logs/q3/e.txt
\end{lstlisting}
\lstinputlisting[caption={Litmus Results (herd7)}, label={lst:MPC}]{../logs/q3/e.txt}
