\section{}
\subsection{(2hr)}

We define $ppo$ to be the communication relation without the 'writes to the same location' relation as a relaxation of x86-TSO. 

\lstinputlisting{../cats/tsorel.cat}

\subsection{(20min)}

$S$ is a good test to verify our model due to its two writes to different memory locations. 
We expect different results in our relaxed model vs. the standard x86-TSO model.

\begin{lstlisting}
    
    diyone7 -arch AArch64 PodWW Rfe PodRW Wse -name S
    herd7 S.litmus -model cats/tsorel.cat>> logs/q4/b1.txt
    herd7 S.litmus > logs/q4/b2.txt 

\end{lstlisting}

Indeed we see that in the relaxed model, we sometimes see the 'reordered' outcome, where in TSO we never see this. 

\lstinputlisting[caption={Litmus Results (herd7) (PPO Model)}, label={lst:tsorel}]{../logs/q4/b1.txt}
\lstinputlisting[caption={Litmus Results (herd7) (x86 TSO Model)}, label={lst:tsorel}]{../logs/q4/b2.txt}

\subsection{(1.5 hr)}
Here is the paper math definition of the relaxed model based on the x86-tso model referenced in \cite{alglave2014herding} and the notes.
I have removed MFENCE and LOCK for clarity. 
$\mathbf{RB}$ and $\mathbf{RM}$ are unchanged, we include $\mathbf{WB}$ definitions and keep the model from the notes otherwise unchanged.
Crucially, we partition the write buffer into a 'skipped' and a 'rest' queue to allow for arbitrary reordering of writes to different locations,
 but we still require that writes to the same location are ordered.

% operational model (not axiomatic)
%\begin{flalign*}
%E &= \{e \mid e \in \{e_1, \dots, e_n\} \land (\text{iswrite}(e) \lor \text{isread}(e))\} & \\
%\text{po} &= \{(e, e') \mid e \in E \land e' \in E \land e < e' \land \text{thread}(e) = \text{thread}(e')\} & \\
%\text{wr} &= \text{po} \land (\text{iswrite}(e) \land \text{isread}(e')) & \\
%\text{ww} &= \text{po} \land \text{iswrite}(e) \land \text{iswrite}(e') \land (\text{addr}(e) \neq \text{addr}(e')) & \\
%\text{ppo} &= \text{po} \setminus (\text{ww} \lor \text{wr}) & \\
%\text{acyclic}& (\text{ppo} \mid \text{com}) \text{as } \text{sc} &
%\end{flalign*}

\begin{flalign*}
\text{Events} \quad e \quad &\mid \quad a:t:\text{W } x=v  \\
&\mid \quad a:t:\text{R } x=v \\
&\mid \quad a:t:\text{Dw } x=v  \\
\text{Memory}\quad  m\quad & \mid \langle M : \text{addr} \to \text{value} \\
              &\mid \quad B : \text{tid}  \to \text{write\_event list} \rangle \\
\text{Operations} \quad o \quad &\mid \quad \mathbf{WB} : m.B(t) = b_{skipped} \mathrel{@} b_{rest} \quad \forall (\dots \text{W } y=v') \in b_{skipped} \ldotp y \neq x \\
&\mid  \quad \quad m \xrightarrow{a:t:\text{W } x=v} m \oplus \langle B := m.B \oplus (t \mapsto (b_{skipped} \mathrel{@} [a:t:\text{W } x=v] \mathrel{@} b_{rest})) \rangle 
\end{flalign*}



\subsection{(1 min)}

C allows for this sort of relaxation natively with stdatomic and memory\_order\_relaxed.
If these are executed with memory\_order\_relaxed on ARM for example, two writes to different locations may be reordered. 
If we wanted to use C 'as it is expected,' the compiler would need to enforce fencing between writes to ensure sequential consistency. 

\subsection{(5 min)}

Arbitrarily reordering of reads from different locations may be more tricky. 
Take Message Passing for example, arbitrary reordering of reads of different locations effectively 
breaks any notion of intrathread communication, and fencing, reliance on atomicity, or at least acquire/release must be used often. 
Realistically, a language without fences, barriers, or sequential reads becomes chaos. 